\documentclass{article}

\usepackage[usenames,dvipsnames]{color}
\usepackage{hw}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{float}
\setlength{\marginparwidth}{2.15cm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[]{algorithm2e}
\usepackage{comment}

%\newcommand{\comment}[1]{\textcolor{blue}{\textsc{\textbf{[#1]}}}}

% Some commands to allow solutions to be embedded in the assignment file.
\ifcsname issoln\endcsname \else \def\issoln{1} \fi
\newcommand{\soln}[1]
{
  \if\issoln 1
  {\color{red}
  \textbf{Solution:}
  #1
  }
  \fi
}

% SOLUTIONS ENVIRONMENT DEFAULT.
\newenvironment{soln2}{\begin{comment}}{\end{comment}}
% TO SHOW SOLUTIONS, include following (else comment out):
%\renewenvironment{soln2}{
%    \leavevmode\color{red}\ignorespaces
%    \textbf{Solution:}
%}{}


\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\st}{\mathrm{s.t.}}

\makeatletter
\newcommand{\removelatexerror}{\let\@latex@error\@gobble}
\makeatother

\begin{document}

\section*{}
\begin{center}
  \centerline{\textsc{\LARGE Homework 1{\if\issoln 1 Solutions \else \fi}}}
  \vspace{0.5em}
  \centerline{\textsc{\Large Probability, Maximum Likelihood Estimation (MLE), Bayes Rule, kNN}}
  \vspace{1em}
  \textsc{\large CMU 10-701: Machine Learning (Fall 2016)} \\
  \url{https://piazza.com/class/is95mzbrvpn63d}
  \centerline{OUT: September 13th}
  \centerline{DUE: September 26th, 11:59 PM}
\end{center}


\section*{START HERE: Instructions}


\begin{itemize*}

\item \textbf{Collaboration policy:} Collaboration on solving the homework is allowed, after you have thought about the problems on your own.  It is also OK to get clarification (but not solutions) from books or online resources, again after you have thought about the problems on your own.  There are two requirements: first, cite your collaborators fully and completely (e.g., ``Jane explained to me what is asked in Question 3.4'').  Second, write your solution {\em independently}: close the book and all of your notes, and send collaborators out of the room, so that the solution comes from you only.

\item\textbf{Late Submission Policy:} You will be allowed 2 total late days without penalty for the entire semester. You may be late by 1 day on two different homeworks or late by 2 days on one homework. Weekends and holidays are also counted as late days. Late submissions are automatically considered as using late days.
\\Once those days are used, you will be penalized according to the following policy:
\begin{itemize}
\item Homework is worth full credit before the deadline.
\item It is worth half credit for the next 24 hours.
\item It is worth zero credit after that.
\end{itemize}
You must turn in at least $n-1$ of the $n$ homeworks, even if for zero credit, in order to pass the course.


\item\textbf{Submitting your work:} Assignments should be submitted as PDFs using Gradescope unless explicitly stated otherwise.  Each derivation/proof should be completed on a separate page. Submissions can be handwritten, but should be labeled and clearly legible.  Else, submissions can be written in LaTeX.  Upon submission, label each question using the template provided by Gradescope.  

 \item \textbf{Programming}: All programming portions of the assignments should be submitted to Autolab.  We will not be using this for autograding, but rather for plagiarism detection, meaning you may use any language which you like to submit.
\end{itemize*}

\newpage

\input{problem1}
\input{problem2}
\input{problem3}
\input{problem4}
\input{problem5}


\end{document}